Meta-analysis

### 2019-08-01 03_Preliminary_analysis.Rmd
nl
Update after meeting with Adam

   1) Fungicide type
   2) Fungicide dose
   3) row spacing
   4) Host cultivars
   5) Experiment location
   6) Final disease rating

>>>>

   1) Fungicide type
   2) Fungicide dose
   3) row spacing
   4) Host cultivars (probably is a covariate with season due to changing cultivars over time)
   5) Experiment location
   6) Final disease rating

### 2019-08-01 05_MetaAnalysis.Rmd
Update after meeting with Adam

```{r Meta_dataImport}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.)
library(dplyr)
#str(PM_MB_means)
```

@@

### Fungicide Doses
All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
```{r Tebe_dose}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
   kable()
```

@@

```{r row_spacing}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   group_by(row_spacing,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()

@@

@@

for(i in PM_MB_means$Trial_ref){

log(V)[i] = a + b * log(
   mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
        subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
# need to know what parameters a and b are here
# I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
}

@@

library(lme4)

# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMER <- lmer(log(`grain_yield.t.ha.`) ~ Yield_error + 
         (1|Trial_ref), data = PM_MB_train)

@@

library(scales)

@@

PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
}
```

>>>>

```{r Meta_dataImport}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data

#str(PM_MB_means)
```

@@

# How many trials do we have if Tebe and Propi are pooled?

```
Tebeconazole and propiconazole might be able to be pooled as a 'Triazole' fungicide treatment. Amistar is a combination of Azoxistrobin and Cyproconazole. Perhaps Amistar and 200 g/l Tebuconazole + 120 g/l Azoxystrobin might be able to be pooled given they both contain strobins and triazole, however they contain differening dose ratio (inverted).

Perhaps best way forward is to do an analysis of only the Triazoles. Then do another including Amistar as a comparison.

### Fungicide Doses
All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
```{r Tebe_dose}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
   kable()
# why are there zeros
```

@@

```{r row_spacing}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   group_by(row_spacing,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   kable()

@@

```
Were there any statistical diference between all row spacing or only some?  
Can we pool certain row spacings that have no significant difference?

@@

# for(i in PM_MB_means$Trial_ref){
# 
# log(V)[i] = a + b * log(
#    mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
#         subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
# # need to know what parameters a and b are here
# # I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
# }

@@

library(lme4)
library(scales)
# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMER <- lmer(log(Yield_error) ~ `grain_yield.t.ha.`+ 
         (1|Trial_ref), data = PM_MB_train)

summary(PM_MB_trianLMER)

@@

@@

PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
print(Sv)
